---
title: "Regression solution"
output: html_document
date: '2022-05-09'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
```

This is assignment is inspired by practices of [Ryan Miller] (https://remiller1450.github.io/).

## Using regression for predicting binary outcome.

The [Donner Party] (https://en.wikipedia.org/wiki/Donner_Party) dataset documents the fate of members of the Donner Party, a group of 45 pioneers whose migration to California was delayed by a series of mishaps which resulted in the group being stranded in the Sierra Nevada mountains.

**Problem**
Predict survival status members of the Donner Party. The target variable is `Survived`.

## Task

Read the data. Pay attention that data has NA values. It's better to convert target variable to factor.
```{r}
# code for reading data

library(caret)
set.seed("1234")
x <- read.csv('donner_party1.csv')
#x <- na.omit(x)
x[is.na(x$Age),]$Age <- mean(x$Age, na.rm = T)
x$Survived <- as.factor(x$Survived)
xsplit <- createDataPartition(x$Survived, p = 0.6, list = FALSE)
trainx <- x[xsplit,]
testx <- x[-xsplit,]

```

For prediction we will use only variables `Sex` and `Age`. 

For predicting binary outcome we will use **Generalized Linear Model** (`method = "glm"`) and **caret package**. 

```{r}
# code for regression

model <- train(Survived~Age+Sex, data = trainx, method="glm", family = "binomial")
pr <- predict(model, newdata = testx)

```

What is your in-sample accuracy? Build a confusion matrix

```{r}
# code for confusion matrix

model
cmat <- confusionMatrix(pr,testx$Survived)
cmat

```
Use a cross-validation with `method = "repeatedcv"`, `number = 5`, `repeats = 10`. Does cross-validation improve the accuracy?

```{r}
# code for cross-validation

tc <- trainControl(method = "repeatedcv", number = 5, repeats = 10)
modelcv <- train(Survived ~ Age + Sex, data = trainx, method = "glm", family = "binomial", trControl = tc)
modelcv
prcv <- predict(modelcv, newdata = testx)
cmatcv <- confusionMatrix(prcv,testx$Survived)
cmatcv

```